\documentclass[dark]{gsf-presentation}

\begin{document}

\begin{frame}[plain]
	\begin{center}
		\textit{\Large Growing Stone Fellowship}

		\Large
		Teaching: Zaydok

		\vspace{5mm}
		\textbf{\Huge For God So Loved The World}

		\vspace{5mm}
		\large
		October 26$^{\text{th}}$, 2024
	\end{center}
\end{frame}

\begin{frame}[plain]{\textbf{\textcolor{SecondColor}{\LARGE Matthew 28:18-19}}}
	\LARGE
	\begin{center}
		And Jesus came and spake unto them, saying,
		All power is given unto me in heaven and in
		earth.

		\vspace{2mm}
		Go ye therefore, and teach all nations, baptizing
		them in the name of the Father, and of the Son, and 
		of the Holy Ghost:
	\end{center}
\end{frame}

\begin{frame}
	
\end{frame}

\begin{frame}[plain]{\textbf{\textcolor{SecondColor}{\LARGE 1 John 2:1-2}}}
	\LARGE
	\begin{center}
		My little children, these things I write to you,
		that ye sin not, And if any man sin, we have an
		advocate with the Father, Jesus Christ the
		righteous.

		\vspace{2mm}
		And he is the propitiation for our sins: and not
		for ours only, but also for the sins of the whole
		world.
	\end{center}
\end{frame}

\begin{frame}[plain]{\textbf{\textcolor{SecondColor}{\LARGE Psalm 72}}}
	\LARGE
	\begin{center}
			
	\end{center}
\end{frame}

\begin{frame}
	\LARGE
	\begin{enumerate}
		\item To bring presents implies seeking peace with the king
		\item Who was the first nation to serve Solomon?
	\end{enumerate}
\end{frame}

\begin{frame}[plain]{\textbf{\textcolor{SecondColor}{\LARGE Psalm 72}}}
	\LARGE
	\begin{center}

	\end{center}
\end{frame}

\begin{frame}
	\LARGE
	\begin{enumerate}
		\item Because all benefit, all bless the king
		\item Connection with Isaiah 2
	\end{enumerate}
\end{frame}

\begin{frame}[plain]{\textbf{\textcolor{SecondColor}{\LARGE Isaiah 2:1-2}}}
	\LARGE
	\begin{center}
		The word of Isaiah the son of Amoz saw concerning
		Judah and Jerusalem.

		\vspace{2mm}

	\end{center}
\end{frame}

\begin{frame}
	\LARGE
	\begin{enumerate}
		\item If it is cold, even a dog wants to be warm
	\end{enumerate}
\end{frame}

\begin{frame}[plain]{\textbf{\textcolor{SecondColor}{\LARGE Acts 17:23-24}}}
	\LARGE
	\begin{center}

	\end{center}
\end{frame}

\begin{frame}
	\begin{enumerate}
		\item All power in the world given to Christ (see Matt. 28)
		\item Christ was in the world, and the world did
			not know him (see John 1)
	\end{enumerate}
\end{frame}

\begin{frame}[plain]{\textbf{\textcolor{SecondColor}{\LARGE Acts 17:25-31}}}
	\LARGE
	\begin{center}

	\end{center}
\end{frame}

\begin{frame}
	\LARGE
	What world is Christ coming to judge?
\end{frame}

\begin{frame}[plain]{\textbf{\textcolor{SecondColor}{\LARGE Romans 8:22}}}
	\LARGE
\end{frame}

\begin{frame}[plain]{\textbf{\textcolor{SecondColor}{\LARGE Mark 16:15}}}
	\LARGE
\end{frame}

\begin{frame}
	\LARGE
	Did not understand the comment
\end{frame}

\begin{frame}[plain]{\textbf{\textcolor{SecondColor}{\LARGE Revelation 21:23-24}}}
	\LARGE
	\begin{center}
		And the city had no need of the sun, neither of
		the moon, to shine in it: for the glory of God
		did lighten it, and the Lamb is the light thereof.

		\vspace{2mm}
		And the \textbf{nations of them which are saved}
		shall walk in the light of it: and the kings of 
		the earth do bring their glory and honour into it.
	\end{center}
\end{frame}

\begin{frame}[plain]{\textbf{\textcolor{SecondColor}{\LARGE Revelation 21:25-27}}}
	\LARGE
	\begin{center}
		And the gates of it shall not be shut at all by day:
		for there shall be no night there.

		\vspace{2mm}
		And they shall bring the glory and honour of the
		\textbf{nations} into it.

		\vspace{2mm}
		And there shall in no wise enter into it any thing
		that defileth, neither whatsoever worketh abomination,
		or maketh a lie: but they which are written in the
		Lamb's book of life.
	\end{center}
\end{frame}

\begin{frame}
	These are the kings of the world. How do we know?
\end{frame}

\begin{frame}[plain]{\textbf{\textcolor{SecondColor}{\LARGE Revelation 16:13-14}}}
	\LARGE
	\begin{center}
		And I saw three unclean spirits like frogs
		come out of the mouth of the dragon, and out
		of the mouth of the beast, and out of the mouth
		of the false prophet.

		\vspace{2mm}
		For they are the spirits of devils, working miracles,
		which go forth unto the 
		\textbf{kings of the earth and of the whole world},
		to gather them to the battle of that great day of
		God Almighty.
	\end{center}
\end{frame}

\begin{frame}
	\LARGE
	Clearly things start with the nation Israel

	But things do not end there

	The world refers to everyone on God's green earth
\end{frame}

\begin{frame}
	\LARGE
	Honest brethren are sometimes wrong

	Sometimes we were wrong
\end{frame}

\end{document}

