%---------------------------------
% Psalm 39 Notes
%
%---------------------------------
% Author:
% R Nate Crummett
%---------------------------------
\documentclass[dark]{gsf-presentation}

\newcommand{\LORD}{L{\fontsize{11}{11}\selectfont{}ORD}}

\begin{document}

\begin{frame}[plain]
	\begin{center}
		\textit{\Large Growing Stone Fellowship}

		\vspace{3mm}
		\textbf{\huge Psalm 39}

		\vspace{5mm}
		\textcolor{SecondColor}{
			\Large
			To the chief musician, even to Jeduthun, a 
			psalm of David
		}

	\end{center}
\end{frame}

\setcounter{framenumber}{0}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			I said, I will take heed to my ways, that I sin
			not with my tongue: I will keep my mouth with
			a bridle, while the wicked is before me.
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			אמרתי אשמרה דרכי מחטוא בלשוני אשמרה לפי מחסום 
			בעד רשע לנגדי
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			I was dumb with silence, I held my peace,
			even from good; and my sorrow was stirred.
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			נאלמתי דומיה החשיתי מטוב וכאבי נעכר
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			My heart was hot within me, while I was musing
			the fire burned: then spake I with my tongue,
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			חם לבי בקרבי בהגיגי תבער אש דברתי בלשוני 
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			\LORD{}, make me to know mine end, and
			the measure of my days, what it is; that I may
			know how frail I am.
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			הודיעני יהוה קצי ומדת ימי מה היא
			אדעה מה חדל אני
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			Behold, thou hast made my days as an handbreadth;
			and mine age is as nothing before thee: verily 
			every man at his best state is altogether vanity.
			\textit{Selah}.
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			הנה טפחות נתתה ימי וחלדי כאין נגדך
			אך כל הבל כל אדם נצב סלה
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			Surely every man walketh in a vain shew: surely
			they are disquieted in vain: he heapeth up riches,
			and knoweth not who shall gather them.
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			אך בצלם יתהלך איש אך הבל יהמיון
			יצבר ולא ידע מי אספם
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			And now, Lord, what wait I for? my hope is in thee.
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			ועתה מה קויתי אדני תוחלתי לך היא
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			Deliver me from all my transgressions:
			make me not the reproach of the foolish.
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			מכל פשעי הצילני חרפת נבל אל תשימני
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			I was dumb, I opened not my mouth;
			because thou didst it.
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			נאלמתי לא אפתח פי כי אתה עשית
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			Remove thy stroke away from me: I am
			consumed by the blow of thine hand.
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			הסר מעלי נגעך מתגרת ידך אני כליתי
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			When thou with rebukes dost correct man
			for iniquity, thou makest his beauty to
			consume away like a moth: surely every man
			is vanity. \textit{Selah}.
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			בתוכחות על עון יסרת איש ותמס כעש
			חמודו אך הבל כל אדם סלה
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			Hear my prayer, O \LORD{}, and give ear unto
			my cry; hold not thy peace at my tears: for I
			am a stranger with thee, and a sojourner, as
			all my fathers were.
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			שמעה תפלתי יהוה ושועתי הכזינה אל דמעתי אל
			תחרש כי גר אנכי עמך תושב ככל אבותי
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}
	\LARGE
	\begin{english}
		\begin{center}
			O spare me, that I may recover strength, before
			I go hence, and be no more.
		\end{center}
	\end{english}

	\begin{hebrew}
		\begin{center}
			השע ממני אבליגה בטרם אלך ואינני
		\end{center}
	\end{hebrew}
\end{frame}

\begin{frame}[allowframebreaks,plain]{References}
	\printbibliography
\end{frame}

\end{document}
